\huge \textbf{Parameter Forecasts From CMB Lensing and Galaxy Lensing Power- and Bispectra}

### 2025-04-11 paper/paper_draft.tex
paper changes

When only considering autospectra the formulas simplify to
\begin{equation*}
    F_{\alpha\beta} = \sum_{l} \sum_{XY}\sum_{X'Y'}(2l+1)\frac{\partial_{\alpha}C_l^{XX} \partial_\beta C^{XX}_l}{(C_l^{XX})^2},
\end{equation*}
and, for bispectra,
\begin{equation*}
    F_{\alpha\beta} = \sum_{l_1 \leq l_2 \leq l_3} \frac{\mathcal P _{l_1l_2l_3}}{6}
    \frac{\partial_\alpha B^{X X X}_{l_1 l_2 l_3} 
    \partial_\beta B^{XXX}_{l_1 l_2 l_3}}{C^{XX}_{l_1}C^{XX}_{l_2}C^{XX}_{l_3}}.
\end{equation*}

\section{Calculation Details}\label{sec:calcdetails}
\subsection{Numerical Considerations}
% I used CAMB, how I took derivative, interpolation, fisher matrix sampling, matter bispectrum in terms of power spectrum

Running cosmological simulations to obtain the matter power spectra and other functions was done with the CAMB package (REF).

To speed up the calculation of the lensing powerspectra and especially the bispectra, an interpolation approach was used. Due to being 3 dimensional, it was not feasible to interpolate the lensing bispectrum directly. We instead chose to interpolate all 1 and 2 dimensional functions that the bispectra are based on and then calculate the bispectra with the interpolated functions instead. This significantly sped up the computation at the cost of small errors in the values in the bispectrum ($\sim 1\%$) when compared with the uninterpolated values.

The time complexity of the Fisher matrix scales with the maximum multipole considered, $l_{max}$, as $\mathcal O (l_{max}^3)$, leading to time issues for realistic values of $l_{max}$. We thus calculated the $l_1 < l_2 < l_3$ part of each Fisher matrix element (see the appendix) by sampling every step of 10 %(CHECK IF THIS IS STILL CORRECT BEFORE PUBLISHING) 
in $l_1$ and $l_2$. Due to the discontinuos nature of the bispectrum (e.g. it vanishes immediately if $l_1 + l_2 + l_3$ is and odd number) we didn't sample $l_3$ values. This was done similarly in (REF).

\subsection{Choosing Experimental Parameters}

% lmin, lmax, galaxy redshift distribution, fiducial values (!), noise levels, 
% for SO, CMB - S4, Euclid, LSST
We chose our fiducial cosmology in line with the results from the Planck mission \cite{planckresults}.
\begin{align*}
    H_0 &= 67.4 \, \text{km/s/Mpc}, && \text{(Hubble constant)} \\
    \Omega_b h^2 &= 0.0224, && \text{(Physical baryon density parameter)} \\
    \Omega_c h^2 &= 0.120, && \text{(Physical cold dark matter density parameter)} \\
    n_s &= 0.965, && \text{(Scalar spectral index)} \\
    A_s &= 2.1 \times 10^{-9}, && \text{(Amplitude of primordial scalar fluctuations)} \\
    \sum m_\nu &= 0.06 \, \text{eV}, && \text{(Sum of neutrino masses)} \\
    w_0 &= -1. && \text{(Dark energy equation of state parameter)}
\end{align*}

@@

    e^{i\mathbf k \cdot \hat {\mathbf n}\chi}=4\pi\sum_{lm}i^lj_l(k\chi )Y_l^m(\hat{\mathbf n})^*Y_l^m(\hat{\mathbf k}) = 4\pi\sum_{lm}i^lj_l(k\chi )Y_l^m(\hat{\mathbf n})Y_l^m(\hat{\mathbf k})^*,

@@

To further evaluate the integral we will make the standard \textbf{Limber approximation}. The Bessel functions peak sharply at $l=x$\footnote{Some sources use $x\approx l+1/2$ instead, which is slightly more accurate for larger scales (low $l$) and slightly less accurate for smaller scales.}, with the peak being increasingly sharp for higher $l$. Similarly to $\delta(x-x_0)f(x)=\delta(x-x_0)f(x_0)$, we thus take $j_l(k\chi)f(k)\approx j_l(k\chi)f(l/\chi)$. The Bessel functions satisfy an orthogonality condtion,

@@

    = \frac{1}{l^3\pi}\int_0^{\chi_*}\chi\d \chi W(\chi)^2 P_\psi(l/\chi,\eta_0 - \chi, \eta_0-\chi).

@@

Now using the identity REF for the complex exponential:

@@

The definition for the bispectrum of any set of randomly distributed spherical harmonic components $X^k_{lm}$ is CITE Hu 2000 
\begin{equation*}
    \langle (X_1)_{l_1m_1}(X_2)_{l_2m_2}(X_3)_{x_3m_3} \rangle = \begin{pmatrix}
        l_1 & l_2 & l_3 \\ m_1 & m_2 & m_3
    \end{pmatrix}
    B_{l_1l_2l_3}^{X_1X_2X_3}.
\end{equation*}
Note the independence on $m_i$, this necesarilly follows from statistical isotropy. % TODO: add a short explanation here
If $m_1+m_2+m_3\neq 0$, the associated Wigner-3j symbol vanishes and the bispectrum is set to zero.
Also note that in this definition we have immediately generalized to include cross correlation between different fields $X_1$, $X_2$, $X_3$. This will be relevant later when we look at cross correlations between shear and convergence fields.

Using the above definition and the symmetry property
\begin{equation*}
    \begin{pmatrix}
        l_1 & l_2 & l_3\\
        -m_1 & -m_2 & -m_3
      \end{pmatrix}
      =
      (-1)^{l_1+l_2+l_3}
      \begin{pmatrix}
        l_1 & l_2 & l_3\\
        m_1 & m_2 & m_3
      \end{pmatrix}
\end{equation*}
we find
\begin{gather*}
    B^{\psi_1\psi_2\psi_3}_{l_1l_2l_3}
    = (-1)^{l_1+l_2+l_3}
    \sqrt{\frac{(2l_1 + 1)(2l_2 + 1)(2l_3 + 1)}{4\pi}} \begin{pmatrix} l_1 & l_2 & l_3 \\ 0 & 0 & 0 \end{pmatrix}
    (2\pi)^3 8 \\
    \times \int \chi^2\d \chi\prod_i\br{-2 W_i(\chi, \chi_*)\frac{1}{(2\pi)^{3}}\frac{\pi}{2\chi^2}4\pi (-1)^{l_i}} B^\Psi(\{l_i/\chi\}, \{\eta_0-\chi\}),
\end{gather*}
where we were able to drop the $(-1)^{m_1+m_2+m_3}$ factor due to the bispecrum vanishing if that sum doesn't equal $0$, as mentioned earlier. When all $m_i$ equal zero, the Wigner 3j-symbol gains a number of useful properties % TODO: discuss all of them
In particular, it vanishes if $l_1+l_2+l_3$ is odd, meaning we can drop the $(-1)^{l_1+l_2+l_3}$ factor. Additionally cancelling common factors then gives
\begin{align*}
    B^{\psi_1\psi_2\psi_3}_{l_1l_2l_3}
    =
    -\sqrt{\frac{(2l_1 + 1)(2l_2 + 1)(2l_3 + 1)}{4\pi}} \begin{pmatrix} l_1 & l_2 & l_3 \\ 0 & 0 & 0 \end{pmatrix} 8 \int \frac{\d \chi }{\chi^4} W_1(\chi)W_2(\chi)W_3(\chi) B^\Psi(\{l_i/\chi\}, \eta_0-\chi).
\end{align*}

@@

% TODO: mention that the definition of the bispectrum is different form power spectrum of Psi in terms of normalization constant
% TODO: explain 3d dirac delta in terms of spherical harmonics (eq 78 thesis Luna)
% TODO: explain that we used that int d^2 Omega Y Y Y = A_vec l^vec m (eq 82 thesis Luna)
% using that d^3 k = k^2 d k d^2 Omega_k
% TODO: fix this
\subsection{Gravitational potential spectra in terms of matter spectra}
% TODO: fix references and citations 
To convert equations ... and ... to forms that we can directly evaluate we will need to replace the spectra of the graviational potential with matter spectra. Specifically, we define the matter power spectrum in agreement with the CAMB package documentation CITE and the matter bispectrum in agreement with CITE FITTING FUNC PAPER such that we can approximate it in terms of the matter power spectrum using hyperextended perturbation theory. The \textbf{density contrast} is defined as
\begin{equation}
    \delta(\mathbf x) := \frac{\rho(\mathbf x)-\bar \rho}{\bar\rho},
\end{equation}
and the matter spectra are defined in terms of the fourier transformed density contrast $\delta(\mathbf k)$ as 
\begin{gather*}
    \langle \delta(\mathbf k, \eta) \delta(\mathbf k', \eta)^* \rangle = (2\pi)^3\delta(\mathbf k - \mathbf k')P^\delta(\mathbf k, \eta),\\
    \langle \delta(\mathbf k_1, \eta) \delta(\mathbf k_2, \eta) \delta(\mathbf k_3, \eta) \rangle = (2\pi)^3\delta(\mathbf k_1 + \mathbf k_2 + \mathbf k_3)B^\delta(k_1, k_2, k_3, \eta).
\end{gather*}
The mean matter density of the universe, \( \bar{\rho} \), can be expressed in terms of the matter density parameter \( \Omega_m \) and the critical density \( \rho_c \) as 
$$
\bar{\rho}(\eta) = \frac{3 \Omega_m H_0^2}{8 \pi G}\frac{1}{a(\eta)^3},
$$
where $a(\eta)$ is the only time dependent factor on the right hand side.
In the case of a flat universe ($K=0$) we can thus rewrite the Poisson equation REF as
% in modern cosm eq 6.41 they say - nabla^2 Phi = ..., however here we use Psi instead and Psi = - Phi in our regime so hence why we don't take the - sign
\begin{equation}
    \nabla^2\Psi = 4\pi G a^2\br{\frac{3\Omega_m H_0^2}{8\pi G}\frac{1}{a^3}}\delta = \frac{3\Omega_m H_0^2}{2} \frac{1}{a}\delta \implies \Psi(k, \eta) = -\frac{3\Omega_m H_0^2}{2}\frac{1}{a}\frac{\delta(k, \eta)}{k^2},
\end{equation}
where $\Psi(k,\eta)$ and $\delta(k,\eta)$ are functions in Fourier space. For the power- and bispectra we find
\begin{gather*}
    \langle \Psi(\mathbf k, \eta)\Psi^*(\mathbf k',\eta)\rangle = \frac{2\pi^2}{k^3}P^\Psi(k, \eta)\delta(\mathbf k - \mathbf k') \implies P^\Psi(k,\eta) = \frac{1}{k}(9\Omega_m^2H_0^4\pi) \frac{1}{a^2}P^\delta(k,\eta),\\
    \langle \Psi(\mathbf k_1, \eta)\Psi(\mathbf k_2,\eta)\Psi(\mathbf k_3,\eta)\rangle = -(2\pi)^3\delta(\mathbf k_1 + \mathbf k_2 + \mathbf k_3)B^\Psi(k_1,k_2,k_3, \eta)\\ 
    \implies B^\Psi(k_1,k_2,k_3, \eta) = -\frac{1}{k_1^2k_2^2k_3^2}\br{\frac{3\Omega_m H_0^2}{2}}^3 \frac{1}{a^3}B^\delta(\{k_i\}, \eta).
\end{gather*}
We conclude this section by using the above equations to rewrite the lensing potential spectra (equations REF and REF) in terms of matter spectra 
\begin{empheq}[box=\fbox]{align*}
    P^{\psi_X\psi_Y}_l
    & = \frac{9}{l^4}\Omega_m^2H_0^4\int_0^{\chi_*} \chi^2 \d\chi a(\eta_0-\chi)^{-2}W_X(\chi)W_Y(\chi)P^\delta(l/\chi,\eta_0-\chi),\\
    B^{\psi_X\psi_Y\psi_Z}_{l_1l_2l_3} &= \sqrt{\frac{(2l_1 + 1)(2l_2 + 1)(2l_3 + 1)}{4\pi}} \begin{pmatrix} l_1 & l_2 & l_3 \\ 0 & 0 & 0 \end{pmatrix} \frac{27}{l_1^2l_2^2l_3^2}\Omega_m^3H_0^6\\
    & \quad \times \int \chi^2\d \chi a(\eta_0-\chi)^{-3}W_X(\chi)W_Y(\chi)W_Z(\chi)  B^\delta(\{l_i/\chi\}, \eta_0-\chi).
\end{empheq}

>>>>

When only considering autospectra the formulas simplify to
\begin{equation*}
    F_{\alpha\beta} = \sum_{l} \sum_{XY}\sum_{X'Y'}\frac{2l+1}{2}\frac{\partial_{\alpha}C_l^{XX} \partial_\beta C^{XX}_l}{(C_l^{XX})^2},
\end{equation*}
and, for bispectra,
\begin{equation*}
    F_{\alpha\beta} = \sum_{l_1 \leq l_2 \leq l_3} \frac{\mathcal P _{l_1l_2l_3}}{6}
    \frac{\partial_\alpha B^{X X X}_{l_1 l_2 l_3} 
    \partial_\beta B^{XXX}_{l_1 l_2 l_3}}{C^{XX}_{l_1}C^{XX}_{l_2}C^{XX}_{l_3}}.
\end{equation*}

\section{Calculation Details}\label{sec:calcdetails}
% \subsection{Numerical Considerations}
% % I used CAMB, how I took derivative, interpolation, fisher matrix sampling, matter bispectrum in terms of power spectrum

% Running cosmological simulations to obtain the matter power spectra and other functions was done with the CAMB package (REF).

% To speed up the calculation of the lensing powerspectra and especially the bispectra, an interpolation approach was used. Due to being 3 dimensional, it was not feasible to interpolate the lensing bispectrum directly. We instead chose to interpolate all 1 and 2 dimensional functions that the bispectra are based on and then calculate the bispectra with the interpolated functions instead. This significantly sped up the computation at the cost of small errors in the values in the bispectrum ($\sim 1\%$) when compared with the uninterpolated values.

% The time complexity of the Fisher matrix scales with the maximum multipole considered, $l_{max}$, as $\mathcal O (l_{max}^3)$, leading to time issues for realistic values of $l_{max}$. We thus calculated the $l_1 < l_2 < l_3$ part of each Fisher matrix element (see the appendix) by sampling every step of 10 %(CHECK IF THIS IS STILL CORRECT BEFORE PUBLISHING) 
% in $l_1$ and $l_2$. Due to the discontinuos nature of the bispectrum (e.g. it vanishes immediately if $l_1 + l_2 + l_3$ is and odd number) we didn't sample $l_3$ values. This was done similarly in (REF).

% \subsection{Choosing Experimental Parameters}

% lmin, lmax, galaxy redshift distribution, fiducial values (!), noise levels, 
% for SO, CMB - S4, Euclid, LSST
We chose our fiducial cosmology in line with the results from the Planck mission \cite{planckresults}.
\begin{align*}
    H_0 &= 67.4 \, \text{km/s/Mpc}, && \text{(Hubble constant)} \\
    \Omega_b h^2 &= 0.0223, && \text{(Physical baryon density parameter)} \\
    \Omega_c h^2 &= 0.119, && \text{(Physical cold dark matter density parameter)} \\
    n_s &= 0.965, && \text{(Scalar spectral index)} \\
    A_s &= 2.13 \times 10^{-9}, && \text{(Amplitude of primordial scalar fluctuations)} \\
    \sum m_\nu &= 0.06 \, \text{eV}, && \text{(Sum of neutrino masses)} \\
    w_0 &= -1. && \text{(Dark energy equation of state parameter)}
\end{align*}

@@

    e^{i\mathbf k \cdot \hat {\mathbf n}\chi}=4\pi\sum_{lm}i^lj_l(k\chi )Y_l^m(\hat{\mathbf n})^*Y_l^m(\hat{\mathbf k}) = 4\pi\sum_{lm}i^lj_l(k\chi )Y_l^m(\hat{\mathbf n})Y_l^m(\hat{\mathbf k})^*, \label{eq:complexexp}

@@

To further evaluate the integral we will make the standard \textbf{Limber approximation}. The Bessel functions peak sharply at $l=x$\footnote{Some sources use $x\approx l+1/2$ instead, which is slightly more accurate for larger scales (low $l$) and slightly less accurate for smaller scales.}, with the peak being increasingly sharp for higher $l$. Similarly to $\delta(x-x_0)f(x)=\delta(x-x_0)f(x_0)$, we thus take $j_l(k\chi)f(k)\approx j_l(k\chi)f(l/\chi)$. The Bessel functions satisfy an orthogonality condition,

@@

    = \frac{1}{l^3\pi}\int_0^{\chi_*}\chi\d \chi W(\chi)^2 P_\psi(l/\chi,\eta_0 - \chi, \eta_0-\chi). \label{eq:lpsintermsofpsi}

@@

Now using equation \ref{eq:complexexp} to rewrite the complex exponential:

@@

The definition for the bispectrum of any set of randomly distributed spherical harmonic components $X^k_{lm}$ is \cite{Hu2000}
\begin{equation*}
    \langle (X_1)_{l_1m_1}(X_2)_{l_2m_2}(X_3)_{x_3m_3} \rangle = \begin{pmatrix}
        l_1 & l_2 & l_3 \\ m_1 & m_2 & m_3
    \end{pmatrix}
    B_{l_1l_2l_3}^{X_1X_2X_3}.
\end{equation*}
Note the independence on $m_i$, this necesarilly follows from statistical isotropy. % TODO: add a short explanation here
If $m_1+m_2+m_3\neq 0$, the associated Wigner-3j symbol vanishes and the bispectrum is set to zero.
Also note that in this definition we have immediately generalized to include cross correlation between different fields $X_1$, $X_2$, $X_3$. This will be relevant later when we look at cross correlations between shear and convergence fields.

Using the above definition and the symmetry property
\begin{equation*}
    \begin{pmatrix}
        l_1 & l_2 & l_3\\
        -m_1 & -m_2 & -m_3
      \end{pmatrix}
      =
      (-1)^{l_1+l_2+l_3}
      \begin{pmatrix}
        l_1 & l_2 & l_3\\
        m_1 & m_2 & m_3
      \end{pmatrix}
\end{equation*}
we find
\begin{gather*}
    B^{\psi_1\psi_2\psi_3}_{l_1l_2l_3}
    = (-1)^{l_1+l_2+l_3}
    \sqrt{\frac{(2l_1 + 1)(2l_2 + 1)(2l_3 + 1)}{4\pi}} \begin{pmatrix} l_1 & l_2 & l_3 \\ 0 & 0 & 0 \end{pmatrix}
    (2\pi)^3 8 \\
    \times \int \chi^2\d \chi\prod_i\br{-2 W_i(\chi, \chi_*)\frac{1}{(2\pi)^{3}}\frac{\pi}{2\chi^2}4\pi (-1)^{l_i}} B^\Psi(\{l_i/\chi\}, \{\eta_0-\chi\}),
\end{gather*}
where we were able to drop the $(-1)^{m_1+m_2+m_3}$ factor due to the bispecrum vanishing if that sum doesn't equal $0$, as mentioned earlier. When all $m_i$ equal zero, the Wigner 3j-symbol gains a number of useful properties % TODO: discuss all of them
In particular, it vanishes if $l_1+l_2+l_3$ is odd, meaning we can drop the $(-1)^{l_1+l_2+l_3}$ factor. Additionally cancelling common factors then gives
\begin{align}
    B^{\psi_1\psi_2\psi_3}_{l_1l_2l_3}
    =
    -\sqrt{\frac{(2l_1 + 1)(2l_2 + 1)(2l_3 + 1)}{4\pi}} \begin{pmatrix} l_1 & l_2 & l_3 \\ 0 & 0 & 0 \end{pmatrix} 8 \int \frac{\d \chi }{\chi^4} W_1(\chi)W_2(\chi)W_3(\chi) B^\Psi(\{l_i/\chi\}, \eta_0-\chi). \label{eq:lbsintermsofpsi}
\end{align}

@@

% TODO: mention that the definition of the bispectrum is different form power spectrum of Psi in terms of normalization constant
% TODO: explain 3d dirac delta in terms of spherical harmonics (eq 78 thesis Luna)
% TODO: explain that we used that int d^2 Omega Y Y Y = A_vec l^vec m (eq 82 thesis Luna)
% using that d^3 k = k^2 d k d^2 Omega_k
% TODO: fix this
\subsection{Gravitational potential spectra in terms of matter spectra}
% TODO: fix references and citations 
We can rewrite equations \ref{eq:lpsintermsofpsi} and \ref{eq:lbsintermsofpsi} in terms of the matter spectra instead of the graviational potential spectra using the poisson equation. This then allows us to numerically evaluate these objects using CAMB. The \textbf{density contrast} is defined as
\begin{equation}
    \delta(\mathbf x) := \frac{\rho(\mathbf x)-\bar \rho}{\bar\rho},
\end{equation}
and the matter spectra are defined in terms of the fourier transformed density contrast $\delta(\mathbf k)$ as 
\begin{gather*}
    \langle \delta(\mathbf k, \eta) \delta(\mathbf k', \eta)^* \rangle = (2\pi)^3\delta(\mathbf k - \mathbf k')P^\delta(\mathbf k, \eta),\\
    \langle \delta(\mathbf k_1, \eta) \delta(\mathbf k_2, \eta) \delta(\mathbf k_3, \eta) \rangle = (2\pi)^3\delta(\mathbf k_1 + \mathbf k_2 + \mathbf k_3)B^\delta(k_1, k_2, k_3, \eta).
\end{gather*}
The mean matter density of the universe, \( \bar{\rho} \), can be expressed in terms of the matter density parameter \( \Omega_m \) and the critical density \( \rho_c \) as 
$$
\bar{\rho}(\eta) = \frac{3 \Omega_m H_0^2}{8 \pi G}\frac{1}{a(\eta)^3},
$$
where $a(\eta)$ is the only time dependent factor on the right hand side.
In the case of a flat universe ($K=0$) we can thus rewrite the Poisson equation \cite{dodelson2020modern} as
% in modern cosm eq 6.41 they say - nabla^2 Phi = ..., however here we use Psi instead and Psi = - Phi in our regime so hence why we don't take the - sign
\begin{equation}
    \nabla^2\Psi = 4\pi G a^2\br{\frac{3\Omega_m H_0^2}{8\pi G}\frac{1}{a^3}}\delta = \frac{3\Omega_m H_0^2}{2} \frac{1}{a}\delta \implies \Psi(k, \eta) = -\frac{3\Omega_m H_0^2}{2}\frac{1}{a}\frac{\delta(k, \eta)}{k^2},
\end{equation}
where $\Psi(k,\eta)$ and $\delta(k,\eta)$ are functions in Fourier space. For the power- and bispectra we find
\begin{gather*}
    \langle \Psi(\mathbf k, \eta)\Psi^*(\mathbf k',\eta)\rangle = \frac{2\pi^2}{k^3}P^\Psi(k, \eta)\delta(\mathbf k - \mathbf k') \implies P^\Psi(k,\eta) = \frac{1}{k}(9\Omega_m^2H_0^4\pi) \frac{1}{a^2}P^\delta(k,\eta),\\
    \langle \Psi(\mathbf k_1, \eta)\Psi(\mathbf k_2,\eta)\Psi(\mathbf k_3,\eta)\rangle = -(2\pi)^3\delta(\mathbf k_1 + \mathbf k_2 + \mathbf k_3)B^\Psi(k_1,k_2,k_3, \eta)\\ 
    \implies B^\Psi(k_1,k_2,k_3, \eta) = -\frac{1}{k_1^2k_2^2k_3^2}\br{\frac{3\Omega_m H_0^2}{2}}^3 \frac{1}{a^3}B^\delta(\{k_i\}, \eta).
\end{gather*}
Finally, we obtain:
\begin{empheq}[box=\fbox]{align*}
    P^{\psi_X\psi_Y}_l
    & = \frac{9}{l^4}\Omega_m^2H_0^4\int_0^{\chi_*} \chi^2 \d\chi a(\eta_0-\chi)^{-2}W_X(\chi)W_Y(\chi)P^\delta(l/\chi,\eta_0-\chi),\\
    B^{\psi_X\psi_Y\psi_Z}_{l_1l_2l_3} &= \sqrt{\frac{(2l_1 + 1)(2l_2 + 1)(2l_3 + 1)}{4\pi}} \begin{pmatrix} l_1 & l_2 & l_3 \\ 0 & 0 & 0 \end{pmatrix} \frac{27}{l_1^2l_2^2l_3^2}\Omega_m^3H_0^6\\
    & \quad \times \int \chi^2\d \chi a(\eta_0-\chi)^{-3}W_X(\chi)W_Y(\chi)W_Z(\chi)  B^\delta(\{l_i/\chi\}, \eta_0-\chi).
\end{empheq}
